---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# wkutils

<!-- badges: start -->
<!-- badges: end -->

Whereas the [wk package](https://paleolimbot.github.io/wk/) provides headers and class definitions for well-known geometry formats, this package uses those headers to interrogate and transform these vectors. 

## Installation

You can install the released version of wkutils from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wkutils")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/wkutils")
```

## Example

The gist of the functions in this package:

```{r example}
library(wkutils)

wkt_coords("POINT (30 10)")
coords_point_translate_wkt(30, 10)
wkt_debug("POINT (30 10)")
wkt_set_srid("POINT (30 10)", 1234)
wkt_set_z("POINT (30 10)", 1234)
wkt_meta("POINT (30 10)")
wkt_ranges("POINT (30 10)")
```

The package also contains plot methods for `wk::wkb()` and `wk::wkt()` vectors. These aren't intended to be high-performance, but are helpful for debugging geometries.

```{r wkt-plot}
plot(wk::wkt("LINESTRING (1 2, 4 7)"))
plot(wk::wkt("POINT (3 4)"), add = T)
```

Finally, the package contains slightly faster functions to send points, lines, and polygons to a graphics device:

```{r wk-draw}
nc_sf <- sf::read_sf(system.file("shape/nc.shp", package = "sf"))
nc_wkb <- wk::as_wkb(sf::st_as_binary(nc_sf$geometry))
wkb_plot_new(nc_wkb)
wkb_draw_polypath(nc_wkb)
```
